A* with Perfect Potentials

### 2020-06-11 paper/ch_potentials.tex
foo

As detailed in the previous section, the reasons why flexibility is a necessary property of a routing engine are sheer endless.
However, a formal problem specification that encompasses all these options is complex and well beyond the scope of this paper.
For an example of such a formulation, we refer to \cite{kswz-erptd-20} which covers a truck-specific application.
The algorithm presented in \cite{kswz-erptd-20} uses a preliminary version of CH-Potentials.
For simplicity, we limit our exposition to the classical shortest path formulation.
To support algorithm extensions, we avoid two operations that are adverse to generalization.
These are:
(1) traversing an input edge in backward direction, and
(2) combining input weights.
Backward traversal is problematic as a weight can depend on the moment that an edge is entered, which is unknown in a backward search.
Combining input weights can be difficult, if the input weights are more complex objects than scalar values.
For example, when considering historic traffic patterns, the input weights are usually functions \cite{citation needed}.

Our algorithm has one major restriction, it requires the presence of an inflexible scalar weight lower bound for every input edge.
The performance of our algorithm depends on this lower bound being close to the actual weight.
Using the trivial lower bound of zero everywhere, CH-potentials degenerate to an engineered variant of Dijkstra's algorithm.

>>>>

As detailed in the previous section, the reasons why flexibility is a necessary property of a routing engine are sheer endless.
However, a formal problem specification that encompasses all these options is complex and well beyond the scope of this paper.
For an example of such a formulation, we refer to \cite{kswz-erptd-20} which covers a truck-specific application.
The algorithm presented in \cite{kswz-erptd-20} uses a preliminary version of CH-Potentials.
For simplicity, we limit our exposition to the classical shortest path formulation.
To support algorithm extensions, such as time-dependent routing as descibed in Section \ref{sec:predicted-traffic}, we avoid two operations that are adverse to generalization.
These are:
(1) traversing an input edge in backward direction, and
(2) combining input weights.
Backward traversal is problematic as a weight can depend on the moment that an edge is entered, which is unknown in a backward search.
Combining input weights can be difficult, if the input weights are more complex objects than scalar values.
For example, when considering historic traffic patterns, the input weights are usually functions \cite{citation needed}.

Our algorithm has one major restriction, it requires the presence of an inflexible scalar weight lower bound for every input edge.
The performance of our algorithm depends on this lower bound being close to the actual weight.
Using the trivial lower bound of zero everywhere, CH-potentials degenerate to a variant of Dijkstra's algorithm.
